\thetitle

### 2021-05-16 paper/paper.tex
update

\paragraph{Structure.} The rest of the paper is structured as follows. \MS[t]{TODO} The next section
introduces average reward reinforcement learning and presents the used algorithm. For a more
comprehensive discussion of the theoretical foundations we refer to
\citet{schneckenreither2020average}. Section~\ref{sec:Experimental_Evaluation} describes the
simulation model we use to evaluate the approach. The results of the computation experiments are
presented in Section~\ref{sec:Computational}, and Section~\ref{sec:conclusion} concludes the paper.

@@

This section presents related literature and is split into two parts. First we discuss lead time
management literature and second the relevant literature of reinforcement learning.

@@

@@

\section{Average Reward Adjusted Deep RL Algorithm }

@@

@@

\section{Lead Time Setting}

@@

The \textit{action space} is composed of two decisions, the relative change of the lead times to the
currently set lead times $LT_{g} \in \{1,2,\ldots,\DDS\}$ for each product type $\pt$.
%
We restrict the lead time update for state $s_{t+1}$ according to the lead time $LT_{g}$ from state
$s_{t}$ by a maximum change of 1. Thus, if $LT_{g}$ is the current lead time of product type $\pt$
the agent can choose a lead time in $\{1,2,\ldots,\DDS\} \cap \{LT_{g}-1,LT_{g},LT_{g}+1\}$. % Put
% differently the algorithm can increase or decrease the lead time by 1 or leave it as it is, as long
% as it acts within the discrete action space given by the set $\{1,2,\ldots,\DDS\}$ for each product
% type.
A naive approaches is to define one action for each combination of actions over all product type.
This however, due to the exponential growth, results in only being able to solve very small
production systems with only few product types. A common solution in production planning is to
aggregate the products into product groups, cf.\@ hierarchical production
planning~\citep{schneeweibeta1995hierarchical}.
%
Although applicable in our setup, if we group the products into bottleneck and non-bottleneck
products as done by \citet{schneckenreither2020order}, also this approach simply does not scale.

\begin{figure*}[t!]
  \centering
  \input{figures/indep_agents}                      % Figure production system
  \caption{Illustration of independent agents as agent one increases the lead time}\label{fig:indep-agents}
\end{figure*}
%
Therefore, in the seek of a broader solution we establish the idea of \textit{independent agents}.
Each independent agent operates on the same system state, but chooses only a part of the actual
executed action. In our case each independent agent is responsible for the lead time update of a
specific product type. To the best of the author's knowledge this is the first work to reduce the
action space in this way. Figure~\ref{fig:indep-agents} illustrates the idea, where wlog.\@ we use
two agents and for simplicity omit the reward and truncate the state to the lead times. Assume that
the first independent agent chooses to increase the lead time from \(3\) to \(4\). Thus, the future
state, seen from this agent, depends on the probability of the other independent agent choosing to
increase (\(\inc\)), decrease (\(\dec\)) or not change (\(\pers\)) the lead time. The Markov
property, that is
\(p(s_{t+1}, r_{t} \mid s_{t}, a_{t}) = p((4,\cdot), r_{t} \mid (3,3), (\inc, \cdot)) \), is not
touched by this adaption. While for the first agent the reward and future state only depends on the
current state and action taken, the corresponding probabilities for future state and reward change
during the learning process as the the agent starts to behave differently.
%
This allows us to investigate the algorithms behaviour for even larger solution spaces. In
particular, this adaption enables us to present the algorithm the above defined state space not only
on the basis of product groups, but directly for each product type \(\pt\). Note that without this
extension the problem is computationally infeasible due to \(3^{6} = 729\) possible actions.
Removing the dependency between the lead times of different product types reduces the set of
possible actions, and thus the number of ANN output layer nodes, to \(3 \cdot 6 = 18\). In
preliminary experiments on small examples we only observed a very slight increase of required steps
during training. Therefore, this is a vital adaption to ensure scalability.

@@

\paragraph*{Optimised Algorithm.}
Our implementation includes several optimisations, that help the algorithm in better exploring the
solution space and stabilise the learning process. These include the above discussed independent
agents that operate on the same state, \(n\)-step learning \citep{mnih2016asynchronous},
% overestimating the average reward \(\avgrew^{\pol}\)
and ensuring to constantly reduce the average reward as searching for policies with higher average
costs is unnecessary. Algorithm~\ref{alg:full}
depicts a detailed view on the algorithm including these extensions and with the objective to
minimise the returned rewards. The idea is the same as in Algorithm~\ref{alg:near}, except that the
action selection procedure is a loop over all independent agents and the implementation of the
n-step logic.
%
The agent first choose an action (steps \(4-5\)), executes the selected action and stores the
experience in the replay memory (step \(6\)) and then samples a mini-batch of experiences each of
length \(nstep\) to improve the policy (steps \(7-21\)). Step \(17\) uses an exponentially smoothed
overestimation (by \(2.5\%\)) of the average reward and rate \(2^{-5}\). All average reward updates
above this overestimation are rejected.

>>>>

\paragraph{Structure.} The rest of the paper is structured as follows. The next section introduces
related literature. Section~\ref{sec:avg} establishes the average reward adjusted deep reinforcement
learning algorithm and the extension to independent agents.
Section~\ref{sec:Experimental_Evaluation} describes the simulation model we use to evaluate the
approach. In Section~\ref{sec:lead} we briefly discuss lead time setting in this paper, while the
results of the computation experiments are presented in Section~\ref{sec:Computational}. Finally
Section~\ref{sec:conclusion} concludes the paper.

@@

This section is split into several parts. First we discuss lead time management literature, then
reinforcement learning applications to lead time management, third we briefly review the relevant
notation to reinforcement learning and finally we present the relevant literature of reinforcement
learning in the rest of the section. The later includes a discussion of discounted reinforcement
learning, average reward reinforcement learning, the Laurent series expansion of the state values,
and finally average reward adjusted reinforcement learning.

@@

\section{Average Reward Adjusted Deep RL Algorithm }\label{sec:avg}

This section presents the average reward adjusted deep reinforcement learning algorithm \ARA{}.
First, we present a basic version, which suffices for small problem sizes and introduce the idea of
independent agents, before presenting an scalable optimised version.

\subsection{Basic Average Reward Adjusted Deep RL Algorithm}

@@

@@

\subsection{Independent Agents}

In our application the agent can update the lead time for each product type by a maximum magnitude
of \(1\) in regard to the lead time of the current period. A naive approaches is to define one
action for each combination of possible lead time updates over all product types, e.g.\@ one action
for a system with six product types could be the vector \(+1, +1, 0, 0, +1, 0\). This however, due
to the exponential growth, results in only being able to solve very small production systems with
only few product types. A common solution in production planning is to aggregate the products into
product groups, cf.\@ hierarchical production planning~\citep{schneeweibeta1995hierarchical}.
%
Although applicable in our setup if we group the products into bottleneck and non-bottleneck
products as done by \citet{schneckenreither2020order}, we refrain from this adaption as it does not
scale to larger sized production systems.

\begin{figure*}[t!]
  \centering
  \input{figures/indep_agents}                      % Figure production system
  \caption{Illustration of independent agents as agent one increases the lead time}\label{fig:indep-agents}
\end{figure*}
%
Therefore, in the seek of a broader solution we establish the idea of \textit{independent agents}.
Each independent agent operates on the same system state, but chooses only a part of the actual
executed action. In our case each independent agent is responsible for the lead time update of a
specific product type. To the best of the author's knowledge this is the first work to reduce the
action space in this way. Figure~\ref{fig:indep-agents} illustrates the idea, where wlog.\@ we use
two agents and for simplicity omit the reward and truncate the state to the lead times. Assume that
the first independent agent chooses to increase the lead time from \(3\) to \(4\). Thus, the future
state, seen from this agent, depends on the probability of the other independent agent choosing to
increase (\(\inc\)), decrease (\(\dec\)) or not change (\(\pers\)) the lead time. The Markov
property, that is
\(p(s_{t+1}, r_{t} \mid s_{t}, a_{t}) = p((4,\cdot), r_{t} \mid (3,3), (\inc, \cdot)) \), is not
touched by this adaption. While for the first agent the reward and future state only depends on the
current state and action taken, the corresponding probabilities for future state and reward change
during the learning process as the agent starts to behave differently.
%
This allows us to investigate the algorithms behaviour for even larger solution spaces. In
particular, this adaption enables us to present the algorithm the above defined state space not only
on the basis of product groups, but directly for each product type \(\pt\). Note that without this
extension the problem is computationally infeasible due to \(3^{6} = 729\) possible actions.
Removing the dependency between the lead times of different product types reduces the set of
possible actions, and thus the number of ANN output layer nodes, to \(3 \cdot 6 = 18\). In
preliminary experiments on small examples we only observed a very slight increase of required steps
during training. Therefore, this is a vital adaption to ensure scalability.

\subsection{Scalable Average Reward Adjusted Deep RL Algorithm}

The basic algorithm above suffices only for problem sets of rather small size due to the
computational complexity and the growth of the action space. In our case, that would either require
a production system with at most \(3\) product types, or an aggregation of product types into
product groups. In the sense of this foundational research paper, we rather aim for an enhanced
version of the algorithm that is scalable.

Therefore, our implementation includes several optimisations, that help the algorithm in better
exploring the solution space and stabilise the learning process. These include the above discussed
independent agents that operate on the same state, \(n\)-step learning \citep{mnih2016asynchronous},
and ensuring to constantly reduce the average reward as searching for policies with higher average
costs is unnecessary. Algorithm~\ref{alg:full} depicts a detailed view on the algorithm including
these extensions and with the objective to minimise the returned rewards. The idea is the same as in
Algorithm~\ref{alg:near}, except that the action selection procedure is a loop over all independent
agents and the implementation of the n-step logic.
%
The agent first chooses an action (steps \(4-5\)), executes the selected action and stores the
experience in the replay memory (step \(6\)) and then samples a mini-batch of experiences each of
length \(nstep\) to improve the policy (steps \(7-21\)). Step \(17\) uses an exponentially smoothed
overestimation (by \(2.5\%\)) of the average reward and rate \(2^{-5}\). All average reward updates
above this overestimation are rejected.

@@

\section{Lead Time Setting}\label{sec:lead}

@@

The \textit{action space} is composed of two decisions, the relative change of the lead times to the
currently set lead times $LT_{g} \in \{1,2,\ldots,\DDS\}$ for each product type $\pt$.
%
We restrict the lead time update for state $s_{t+1}$ according to the lead time $LT_{g}$ from state
$s_{t}$ by a maximum change of 1. Thus, if $LT_{g}$ is the current lead time of product type $\pt$
the agent can choose a lead time in $\{1,2,\ldots,\DDS\} \cap \{LT_{g}-1,LT_{g},LT_{g}+1\}$. % Put
% differently the algorithm can increase or decrease the lead time by 1 or leave it as it is, as long
% as it acts within the discrete action space given by the set $\{1,2,\ldots,\DDS\}$ for each product
% type.

@@
